### 2021-05-19 project_ashish_monograph/CMS.tex
updated

The CMS Run 2 pixel detector consists of four concentric barrel layers (L1-L4) at radii of 29, 68, 109 and 160 mm and three disks (D1-D3) on each end at distances of 291, 396, and 516 mm from the center of the detector. It is built from 1856 segmented silicon sensor modules, where 1184 modules are used in the barrel pixel detector (BPIX) and 672 modules are used for the forward disks (FPIX) . \\

>>>>

The CMS Run 2 pixel detector consists of four concentric barrel layers (L1-L4) at radii of 29, 68, 109 and 160 mm and three forward disks (D1-D3) on each end at distances of 291, 396, and 516 mm from the center of the detector. It is built from 1856 segmented silicon sensor modules, where 1184 modules are used in the barrel pixel detector (BPIX) and 672 modules are used for the forward disks (FPIX) . \\

### 2021-05-19 project_ashish_monograph/PCC.tex
updated

LHC 2018 run can be categorized as follows, \\

@@

Modules which are observed to function efficiently are considered for luminosity calculation. The module veto lists correspond to second Run2018D and select each detector part L2, L3, L4, D1, D2 and D3. Barrel layer 1 (L1) is not used for luminosity determination \cite{vetolist}. \\

>>>>

LHC 2018 run is divided into A, B, C and D as described below. \\

@@

4.Run2018D \\

Run number ranges from 320500 to 323699 \\
Number of runs per period is 262 \\

5. late Run2018D \\

Run number ranges from 320500 to 325175 \\
Number of runs per period is 339 \\

Modules which are observed to function efficiently are considered for luminosity calculation. The module veto lists correspond to late Run2018D that select each detector part barrel layers L2, L3, L4 and forward disks D1, D2, D3. Barrel layer 1 (L1) is not used for luminosity determination \cite{vetolist}. \\
